The evolution of gene expression in the term placenta of viviparous mammals

### 2016-01-04 manuscript/manuscript.Rnw
fix top primate changes table

placenta.lineage.specific.table <- function(analysis,output=TRUE) {
    temp.table <- 
        head(placenta.lineage.specific.analysis[analysis.name==analysis &
                                                p.value <= 0.05][order(p.value),
                                                                 list(human_name,p.value,fdr,fc),],
             n=5)
    temp.table <- data.table(temp.table)
    setkey(temp.table,"human_name")
    temp.table <- 
        hugo.nomenclature[temp.table][,list(`Approved Symbol`,
                                            `Approved Name`,p.value,fdr,fc)]
    setkey(temp.table,"Approved Symbol")
    setnames(temp.table,
              c("Human Symbol","Human Name","p (t-test)","FDR","Fold Change")
              )
    if (output) {
        print(xtable(temp.table[order(p.value),],
                     display=c("s","s","s","e","g","f"),
                     ),
              booktabs=TRUE,
              floating=FALSE,
              math.style.exponents=TRUE,
              sanitize.text.function=genes.table.sanitize,
              include.rownames=FALSE)

    }
    return(invisible(temp.table[order(p.value),]))
}
@

@@

\begin{table}
  \tiny
<<primate.lineage.specific,echo=FALSE,results="asis">>=
pri.all.lin.spec <- NULL
pri.all.lin.spec <- placenta.lineage.specific.table("pri.all")
@ 
\caption{Genes whose expression changed significantly in the primate
  order as compared to all other analyzed species.}
\label{tab:primate_lineage_specific}
\end{table}

>>>>

placenta.lineage.specific.table <- function(analysis,output=TRUE) {
    temp.table <- 
        head(placenta.lineage.specific.analysis[analysis.name==analysis &
                                                p.value <= 0.05][order(p.value),
                                                                 list(human_name,p.value,fdr,fc),],
             n=5)
    temp.table <- data.table(temp.table)
    setkey(temp.table,"human_name")
    temp.table <- 
        hugo.nomenclature[temp.table][,list(`Approved Symbol`,
                                            `Approved Name`,p.value,fdr,fc)]
    setnames(temp.table,
              c("Human Symbol","Human Name","p (t-test)","FDR","Fold Change")
              )
    setkey(temp.table,"Human Symbol")
    if (output) {
        print(xtable(temp.table[order(`p (t-test)`),],
                     display=c("s","s","s","e","g","f"),
                     ),
              booktabs=TRUE,
              floating=FALSE,
              math.style.exponents=TRUE,
              sanitize.text.function=genes.table.sanitize,
              include.rownames=FALSE)

    }
    return(invisible(temp.table[order(`p (t-test)`),]))
}
@

@@

\begin{table}
  \tiny
<<primate.lineage.specific,echo=FALSE,results="asis">>=
pri.all.lin.spec <- placenta.lineage.specific.table("pri.all")
setkey(pri.all.lin.spec,"Human Symbol")
@ 
\caption{Genes whose expression changed significantly in the primate
  order as compared to all other analyzed species.}
\label{tab:primate_lineage_specific}
\end{table}
